\input sys/inputs.tex

\begin{document}

\bigheading{Jumbled password}

% \info{task_name}{infile}{outfile}{points}{timelimit}{memlimit}
% leave this values, if you are not interested
\info{password}{stdin}{stdout}{100}{1000 ms}{1 GB}

Alice is receiving a very secret password. As she's receiving it, she's writing
it down. Oh, look! They are repeating the password once again! Let's write it down
so that we can find any possible mistakes!

And so she's writing it down, when she suddenly realizes that she's made a mistake
in one of the letters! Oh no, she's also lost attention for a short while and she
missed the end of the stream! And to make matters worse, she can't distinguish the
end of the first repetition of the password! Who's gonna help her recover the password?

\heading{Task}

You are given a string $S[0..(n-1)]$ of lower case english letters. Find the first position $i$ in the
string that could mark the start of the password repeat. Formally, find index $i$ satisfying the following conditions:

\begin{enumerate}
    \item $\frac{n}{2} \leq i < n$
    \item There is \textbf{exactly} one-character difference between the
    substrings $S[i\ldots n-1]$ and $S[0\ldots (n - i - 1)]$
    \item Of all the indices satisfying previous two conditions, $i$ is the
    smallest one.
\end{enumerate}

\heading{Input}

The first line of the input contains $n$ ($2 \leq n \leq 200\,000$), the number of characters in the string.
The second line contains string $S$ (consisting of lower case english letters).

\heading{Output}

Output a single line with index $i$ satisfying the conditions. If no such index
exists, output $-1$ instead.

\heading{Samples}


\sampleIN
8
abaaaaaa
\sampleOUT
4
\sampleCOMMENT
The corresponding strings are \texttt{abaa} and \texttt{aaaa}.
\sampleEND


\bigskip


\sampleIN
9
abcdefghi
\sampleOUT
8
\sampleEND

\bigskip

\sampleIN
5
aaaaa
\sampleOUT
-1
\sampleEND

\end{document}
