\input sys/inputs.tex

\begin{document}

\bigheading{Pyramid}

% \info{task_name}{infile}{outfile}{points}{timelimit}{memlimit}
% leave this values, if you are not interested
\info{pyramid}{stdin}{stdout}{100}{2000 ms}{1 GB}

Archaeologists have just deciphered hieroglyphs on walls on a pyramid. Writings
on one of the walls describes $N$ sacred numbers. All numbers which are
divisible by at least one of these numbers are also sacred.

The writings on $M$ other walls claim that the $Q_i$-th lowest sacred number has
magic properties. The archaeologists would like to know which numbers have the
magic properties. Could you help them with that?

\heading{Task}

You are given $N$ positive integers $A_1, A_2, \ldots, A_N$ and $M$ positive
integers $Q_1, Q_2, \ldots, Q_M$. For each $i \in \{ 1, 2, \ldots, M \}$ find the
$Q_i$-th lowest positive integer which is divisible by at least one of the
integers $A_1, A_2, \ldots, A_N$.

\heading{Input}

The first line of the input contains two integers $N$ a $M$. The second line
contains space-separated integers $A_1$, $A_2$, $\ldots$, $A_N$. Then, $M$ lines
follow. Each of them contains an integer $Q_i$.

\bigskip
\noindent
It holds $1 \leq N \leq 15$ and $1 \leq M \leq 50$.\\
For all $i \in \{ 1, 2, \ldots, N \}$ it holds $2 \leq A_i \leq 10^{18}$.\\
For the product of these numbers it holds $A_1 \cdot A_2 \cdot \ldots \cdot A_N \leq 10^{18}$.\\
For all $i \in \{ 1, 2, \ldots, M \}$ it holds $1 \leq Q_i \leq 10^{18}$.\\
Each number on the output is lower than or equal to $10^{18}$.\\
Furthermore, in 10 \% of the testcases $Q_1, Q_2, \ldots, Q_M \leq 10^6$.\\
Furthermore, in 30 \% of the testcases $N \leq 2$.

\heading{Output}

Output $M$ lines. The $i$-th line should contain the $Q_i$-th lowest positive
integer which is divisible by at least one of the integers
$A_1, A_2, \ldots, A_N$.

\heading{Sample}

\sampleIN
5 5
2 5 7 10 11
1
2
3
10
20
\sampleOUT
2
4
5
14
28
\sampleEND

\sampleIN
2 1
70 100
5
\sampleOUT
210
\sampleEND

\end{document}
